    %-------------------------
% Resume in Latex
% Author
% License : MIT
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Edbert Liu} % Your Name
\newcommand{\course}{Masters of Information Technology: Cybersecurity} % Your Program
\newcommand{\roll}{1440026} % Your Roll No.
\newcommand{\phone}{416 617 667} % Your Phone Number
\newcommand{\emaila}{edbert.liuu@gmail.com} %Email 1

\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------

{
\begin{tabularx}{\linewidth}{L r} \\
  \textbf{\Large \name} & {\raisebox{0.0\height}{\footnotesize \faPhone}\ +61 \phone}\\
  {Student No: \roll } & \href{mailto:\emaila}{\raisebox{0.0\height}{\footnotesize \faEnvelope}\ {\emaila}} \\
  Masters of Information Technology: Cyber Security & \href{https://github.com/DoobieD00/Projects}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {github.com/DoobieD00/Projects}} \\  
  {University of Melbourne, Melbourne, Victoria} & \href{https://www.linkedin.com/in/edbertliu/}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {linkedin.com/in/edbertliu/}}
\end{tabularx}
}


%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelors of Information Systems and Finance}{GPA: 3.5}
      {Kelley School of Business, Indiana University, Bloomington, Indiana, United States}{2019-2023}
    \resumeSubheading
        {Associate in Business Administration}{GPA: 3.72}
        {Edmonds College, Edmonds, Washington, United States }{2017-2019}
    \resumeSubHeadingListEnd
    
\vspace{-5.5mm}
%



%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Pentwater Cabinetry}{Lombard, IL, United States}
      {Project Manager}{July 2022 – April 2023}
      \vspace{-2.0mm}
      \resumeItemListStart
    \item {Communicate with clients on a daily basis to coordinate kitchen design projects, providing creative solutions and remodeling according to clients' needs, leading to higher customer satisfaction.}
    \item {Executed outbound sales initiatives by cold calling through CRM, reconnecting with lost customers and addressing their previous concerns, gaining back their businesses and boosting sales by 10\%.}
    \item {Researched customer's needs via carefully constructed surveys to develop data driven pitches and address main points of improvement for the company.}
    \resumeItemListEnd
    
    \vspace{-3.0mm}
    
    \resumeSubheading
      {Kelley Hope Project}{Bloomington, IN, United States}
      {Technology Consultant}{Jan 2022 – July 2022}
      \vspace{-2.0mm}
      \resumeItemListStart
    \item {Implemented website solutions, market research, and social media strategy for 8 small businesses and non-profits to improve online presence, thus alleviating operational barriers created by the COVID-19 pandemic.}
    \item {Managed a rotating team of 4 developers and utilized agile methodologies, scheduled bi-weekly meetings, and delegated tasks to ensure the team meets the client's project goals.}
    \item{Oversee communications and documentation across different sprint teams and the client, establishing clear expectations and requests.}
    \resumeItemListEnd
    
    \vspace{-3.0mm}
      
  \resumeSubHeadingListEnd
\vspace{-5.5mm}

%-----------Positions of Responsibility-----------------
\section{\textbf{Positions of Responsibility}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
    \resumeSubheading
          {Ascend Pan-Asian Leaders}{Bloomington, IN, United States}
          {Director of Technology}{Jul 2020 – Aug 2021}
          \vspace{-2.0mm}
          \resumeItemListStart
        \item {Led multiple 4-week Tech Workshop and taught the basics and functionalities of HTML, SQL, and Tableau to 75+ students establishing a baseline understanding of these common business programming languages.}
        \item {Developed a clean, structured, and cohesive contact database of over 150 alumni to extend the cross-departmental network and strengthen the alumni connection network to enhance the organization's reach and presence.}
        \item {Utilized Wix to modernize the organization's website reflecting updated aesthetics, increasing website traffic and clicks.}
        \resumeItemListEnd
        
        \vspace{-3.0mm}
        
    \resumeSubheading
          {Solar Chapter at Indiana}{Bloomington, IN, United States}
          {Director of Finance and Fundraising}{Apr 2021 – July 2022}
          \vspace{-2.0mm}
          \resumeItemListStart
        \item {Arranged multiple fundraising campaign to garner over \$400+ for the Education and Sanitation for Fatoin project through selling prepacked meals to the people of Bloomington.}
        \item {Generated sponsorship proposals for corporations to raise awareness and gain monetary support (\$5,000) for the Education and Sanitation for Fatoin project, while forming long-lasting partnerships to pursue this social cause together}
        \item {Created detailed progress and final reports for finished projects to inform Sponsors about the work that has been done and how their funds are used, fostering a better trust and lasting relationships.}
        \resumeItemListEnd
    \vspace{-3.0mm}
    
    \resumeSubheading
          {The Indonesian Student Association (PERMIAS)}{Bloomington, IN, United States}
          {Event Organizer/Technical Coordinator}{Mar 2020 – May 2022}
          \vspace{-2.0mm}
          \resumeItemListStart
        \item {Oversaw the technical coordination of a cross-collaborative social event consisting of 10 other PERMIAS organizations and 100+ participants by monitoring and coordinating each Zoom room to ensure a smooth and successful event.}
        \item {Led a team of four to brainstorm 15+ future social events, determining the feasibility of events, creating an inventory list, and logistical plan to streamline operational efficiency and secure long-term organizational influence.}
        \item {Orchestrated the logistics and accommodations of cultural events for approximately 80 people within the Indonesian community to promote cultural diversity and foster camaraderie, while raising cultural awareness to the local community.}
        \resumeItemListEnd
        
        \vspace{-3.0mm}
\resumeSubHeadingListEnd
\vspace{-3mm}

\newpage
%-----------PROJECTS-----------------
\section{\textbf{Personal Projects}}
\resumeSubHeadingListStart
    \resumeProject
      {NBA Team Analysis by Web Scraping} %Project Name
      {Collecting names, teams, and scores of each player in NBA.} %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item {Scraped each NBA team and players in Wikipedia, and kept track of their scores, and team scores}
        \item {Created a table to display the scraped data, and saved it to a file}
        \item {Technology Used: Python, Pandas.}
    \resumeItemListEnd
    \vspace{-2mm}
    
    \resumeProject
      {Front End Website for Globase} %Project Name
      {Created a website for team formation and development.} %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item {Created a functional front end website to assign members into teams to help with their corresponding clients.}
        \item {Technology Used: HTML, CSS.}
    \resumeItemListEnd
    \vspace{-3mm}

    \resumeProject
      {Airplane Departure and Arrival Delay Analysis} %Project Name
      {Created an analysis based on the frequency of delays for Airplanes.} %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item {Analysed frequency of Delays for airplanes from a file.}
        \item {Technology Used : R Studio}
        
    \resumeItemListEnd
      
  \resumeSubHeadingListEnd
\vspace{-8.5mm}

%-----------Technical skills-----------------
\section{\textbf{Technical Skills and Interests}}
 \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, Java, Python, HTML, SQL, CRM.} \\
     \textbf{Libraries }{: C++, Python Libraries. }\\ 
     \textbf{Web Dev Tools}{: Git, Github. } \\ 
     \textbf{Frameworks}{: Burp Suite.} \\
     \textbf{Cloud/Databases}{: Relational Database(mySql). } \\  
     \textbf{Certifications}{: Certified Associate in Project Management (CAPM).}\\
     \textbf{Relevent Coursework}{: Data Structures \& Algorithms, Operating Systems, Object Oriented Programming, Database Management System, Software Engineering, Data Analytics. } \\ 
     \textbf{Areas of Interest}{: Security Analyst, Cloud Security, Technology Consulting.} \\
     \textbf{Soft Skills}{: Problem-Solving, Self-Learner, Presentation, Communication, Project Management, Initiative, Research, Analysis. } \\
     \textbf{Involvements}{: Melbourne Employability Accelerator, FEIT Hackathon }\\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------Achievements-----------------
% \section{\textbf{Achievements}}
%\vspace{-0.4mm}
%\resumeSubHeadingListStart

%\resumePOR{Melbourne Employability Accelerator } % Award
 %    {} % Event
%     {Event dates} %Event Year
    
% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year
     
% \resumeSubHeadingListEnd
 
% \vspace{-5mm}



%-------------------------------------------
\end{document}
